---
title: "England and Wales UK IMD LSOA Maps"
author: "Will Ball"
date: "16/05/2020"
output: 
  html_document:
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(curl)
library(sf)
library(rmapshaper)
library(viridis)
```


## IMD data

Read in straight from source. 'Datazone/LSOA = 'area_code'

```{r, message=FALSE, warning=FALSE}
imd <- read_tsv("https://data.bris.ac.uk/datasets/1ef3q32gybk001v77c1ifmty7x/uk_imd_scores_data.txt")
imd
```

## Shapefile

Read in shapefile for England and Wales and change LSOA Code to 'area_code' for join

```{r}
sf_LSOA <- st_read(
  "https://raw.githubusercontent.com/gausie/LSOA-2011-GeoJSON/master/lsoa.geojson",
                 quiet = TRUE) %>%
  rename(area_code = LSOA11CD)

glimpse(sf_LSOA)

st_geometry(sf_LSOA)
```


## LSOA lookup

Read in lookup for LSOA to Local Authority, rename LSOA code to 'area_code' for join

```{r, warning=FALSE, message=FALSE}
lookup <- read_csv("https://opendata.arcgis.com/datasets/8c05b84af48f4d25a2be35f1d984b883_0.csv") %>% 
  select(LSOA11CD, LAD18CD, LAD18NM) %>% 
  rename(area_code = LSOA11CD)
lookup
```


## Join

Join and then coerce to `sf` object

```{r}
join <- left_join(lookup, imd) %>% 
  left_join(sf_LSOA) %>% 
  st_as_sf(.)
join
```


## Plot

Changes as required:
filter - by LAD18NM/ctry
title - to specify area selected
ggsave - file name

```{r, fig.width=9, fig.height=6}
theme_set(theme_minimal())
join %>% 
  filter(LAD18NM == "Ipswich") %>% 
  ggplot() +                                      
  geom_sf(aes(fill = uk_imd_england_quintile),
          color = NA)+
  scale_fill_viridis(option = "plasma", discrete = T) +
  scale_color_viridis() +
  labs(x = NULL, y = NULL,                                                          
       title = "UK IMD Quintiles for LSOA (2011) in Ipswich",              
       subtitle = "Sources: Abel et al (2016) BMJ Open and Office for National Statistics under 
       Open Government License v3.0",                                                   
       caption = "Plot by @WillBall12 | Contains OS data © Crown copyright and database right (2020)") +  
  theme(axis.line=element_blank(), 
        axis.ticks=element_blank(), 
        axis.text=element_blank(),
        axis.title=element_blank(),
        panel.grid = element_blank(),
        plot.caption.position = 'plot',
        legend.title = element_blank()) 

ggsave("Ipswich.png")
```
